---
title: "Appendix for 'Farmers' risk preferences in eleven European farming systems: A multi-country replication of Bocquého et al. (2014)'"
author: "Jens Rommel, Julian Sagebiel, Marieke Baaken, Jesus Barreiro-Hurle, Douadia Bougherara, Luigi Cembalo, Marija Cerjak, Tajana Čop, Mikołaj Czajkowski, María Espinosa-Goded, Julia Höhler, Laure Kuhfuss, Carl-Johan Lagerkvist, Margaux Lapierre, Marianne Lefebvre, Bettina Matzdorf, Edward Ott, Antonio Paparella, Erika Quendler, Macario Rodriguez-Entrena, Christoph Schulze, Tanja Šumrada, Annika Tensi, Sophie Thoyer, Marina Tomić Maksan, Riccardo Vecchio, Marc Willinger, Katarzyna Zagórska"
date: "October 2022"
always_allow_html: true
output:
  bookdown::html_document2: 
    toc: yes
    toc_float: FALSE
    number_sections: yes
    paged: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, warning=FALSE, message=FALSE)

 #.libPaths( c("/usr/lib/R/library" ,"/usr/local/lib/R/site-library", "/usr/lib/R/site-library"))
 #.libPaths()

 getwd()

 source("main.R")
 

```



\newpage

# Summary statistics per sample

## Raw data lottery choices (cf. Table 1 in main text)

<div style="text-align: justify">

The following tables provide the raw data for the three multiple prices lists (with monotonous switching) by countries. BJR2014 denotes the original study. Note that in the sample from the Netherlands, a few respondents have stopped the survey after the the first and second multiple prices lists. We used these data in the structural models, but not in the mid-point approach. 

</div>

\newpage

### Series 1 

```{r , results='asis'}

### generated in "descriptives.R"
 
series1_freq

```

\
\
\
\
\

\newpage

### Series 2

```{r , results='asis'}
 

series2_freq

```

\
\
\
\
\

\newpage

### Series 3

```{r , results='asis'}
 

series3_freq

```

\
\
\
\
\

\newpage

## Summary statistics for socio-demographic variables by sample

The following table presents, in short form, the number of observations, number of missing observations, mean, and median for each of the samples.

### Socio-demographics by sample

```{r}
kable(desc_soc , digits = 2 ,col.names = c("", "",rep(c("Mean", "SD"), times= (ncol(desc_soc)/2-1) ))) %>% 
  kable_styling(fixed_thead = T) %>% 
  add_header_above(c(" " = 1, " "=1,
  "Age of the subject (years)" = 2,
  "Number of children in the household" = 2,
  "Dummy if education level beyond secondary school" = 2 , "Dummy if self-reported as trusting other people" = 2 , 
  "Total arable area in 100 ha" = 2, 
  "Proportion of land out of the arable area which is owned" =2, 
  "Dummy if the farm is a sole proprietorship or a society with only one associate \n"=2) ,bold = F ,italic = T , align =  "left" ,font_size = "small" , extra_css = 'vertical-align: top' ,line = F) %>% 
    add_header_above(c("Country" = 1, "N"=1, "Age " = 2, "NbChildren" = 2, "EducSup" = 2 , "Trust" = 2 , "Farmsize" = 2, "LandOwned" =2, "IndivOwnder"=2)) 


# as_tibble(cbind(nms = names(c[,-1]), t(c[,-1]))) 
```

\
\
\
\
\

\newpage 

<!-- ### Detailed socio-demographic variables by sample -->




\newpage

# Population statistics and representativeness of samples

<div style="text-align: justify">

In this section, we compare the most recent official Eurostat data from 2016 with our sample data. Some of our samples are not meant to represent the whole country, as they were collected either on a lower regional level or focused on a specific agricultural system (cf. section 3 of this appendix). 

We present national statistics for the variables farm size (utilized arable land and grassland), age, and gender of the farm holder. With respect to farm size, most of our samples contain farms larger than indicated in the Eurostat data. This is also true for the nationwide samples from Austria, Netherlands, Germany, and Sweden. 

The respondents in most samples are younger than in the Eurostat data. The share of female farmers varies. In Sweden, Spain, Netherlands, Germany and France_II the samples are relative representative with respect to gender, the share of female farmers is larger in the samples from Austria, Poland, and Slovenia.

</div>

### Representativeness for farm size (values in percent per size category) 

```{r}

source("prepare_Eurostat.R")

conames <- c("FarmSize", rep(c("Eurostat","Sample"), times=2), "Eurostat", "France_I", "France_II" , rep(c("Eurostat","Sample"), times=7))


kable(table_Size_ours , col.names = conames ) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 1,
  "Austria" = 2,
  "Croatia" = 2,
  "France" = 3 , 
  "Germany" = 2 ,
  "Italy" = 2,
  "Netherlands" =2,
  "Poland"=2,
  "Slovenia" = 2,
  "Spain" = 2,
  "Sweden" = 2) )%>% 
  add_footnote("Eurostat database ef_m_farmang, using the most recent data from 2016." )


```





\
\
\
\
\

\newpage


### Representativeness for age (values in percent per age category)

```{r}

kable(table_Age_ours , col.names = conames ) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 1,
  "Austria" = 2,
  "Croatia" = 2,
  "France" = 3 , 
  "Germany" = 2 ,
  "Italy" = 2,
  "Netherlands" =2,
  "Poland"=2,
  "Slovenia" = 2,
  "Spain" = 2,
  "Sweden" = 2) )%>% 
  add_footnote("Eurostat database ef_m_farmang, using the most recent data from 2016." )


```

\
\
\
\
\

\newpage


### Representativeness for gender (values in percent)

```{r}

kable(table_Sex_ours , col.names = conames ) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 1,
  "Austria" = 2,
  "Croatia" = 2,
  "France" = 3 , 
  "Germany" = 2 ,
  "Italy" = 2,
  "Netherlands" =2,
  "Poland"=2,
  "Slovenia" = 2,
  "Spain" = 2,
  "Sweden" = 2) ) %>% 
  add_footnote("Eurostat database ef_m_farmang, using the most recent data from 2016." )


```

\
\
\
\
\

\newpage



# Short narratives for each sample




## Austria

<div style="text-align: justify">

In Austria, all arable farms who are part of the Integrated Administration and Control System data constituted the population for the survey. The survey region was Lower Austria with approximately 8,700 arable farms. The survey started at the end of September and ended in the beginning of December 2021. During farm advisory meetings for arable farmers the survey was explained, including a screening of the video translated into German. Each of the 194 farmers responded individually, out of which 128 farmers (66 percent) completed the lottery tasks and were used for analysis. All participants were compensated for their participation using vouchers consisting of a fixed payment of 10 Euros (in the form of a meal and a drink) and a payment linked to their choices. Sixty farmers provided an email for payments and the average payment was 11.87 Euro (ranging from 2.90 Euro to 65 Euro). 

</div>

## Croatia

<div style="text-align: justify">

In Croatia, the target group were winegrowers and wine producers from all over Croatia. A list of 637 winegrowers and wine producers was compiled, using publicly available data from web sources. Personalised emails with an invitation link to an online survey were sent to all 637 winegrowers or wine producers in the period from July to September 2021. A video explaining the experimental task was available in Croatian. A total of 130 respondents took part in the survey, of which 120 agreed to participate and 104 completed the survey in full. This results in an effective response rate of approximately 16 percent. 90 respondents (= 87 percent) provided an email address to be eligible for payment. Of all respondents, 70 (= 67 percent) signed up for the debriefing. One in ten participants received a voucher by email. The average value of the voucher was approximately 11 Euro (minimum 7 Euro, maximum 19 Euro). 

</div>

## France_I 

<div style="text-align: justify">

In France, we had two sub-samples collected by two different teams. A video, explaining the experimental task, was available in French in both surveys. The main sub-sample (France I) consisted of potato farmers. They were invited to fill in an online survey through various channels: the link was posted repeatedly on the weekly newsletter of the national potato producer organization, it was also forwarded by emails from cooperatives to their potato-grower members, by the agricultural chamber of the department Pas de Calais, as well as by technical institutes at local and national levels. We do not know how many farmers were reached by the invitations, but we ended up with a final sample of 96 potato farmers. Sixty one farmers signed up for the debriefing. All participants were paid using vouchers. Seventy-nine farmers provided an email for payments and the average payment was 26.36 Euro (ranging from 8.70 Euro to 195 Euro). 

</div>

## France_II

<div style="text-align: justify">

A more limited data collection was organized in the North-West of France (France_II) to gather a convenience sample of organic farmers (vegetable growers, livestock and crops). The survey was promoted through the regional and departmental agricultural chambers of the region Pays de Loire and several networks of organic producers (e.g., GAB, CIVAM, Terre de liens, Bio Loire Océan). A total of 55 persons in close contact with organic farmers were contacted. Those who agreed to help circulate the survey, either forwarded an email by the researchers to organic farmers or promoted the survey in a newsletter. The survey was completed by 28 respondents (24 provided an email address to be eligible for payment and 19 signed up for the debriefing). Payments were made with vouchers to all participants. The average payment was 20 Euro (ranging from 13 Euro to 27 Euro). 

</div>

## Germany

<div style="text-align: justify">

In Germany, data were gathered with the help of an online panel provider specialising in farmer surveys. Using their own panel and another database, they reached out to 12,722 farmers out of which 727 decided to participate in the study. Filter questions at the panel provider's survey tool screened out participants from other German-speaking countries or those not being involved in the decision of the farm. In total, 259 people passed the screening questions and opened the questionnaire, out of which 153 provided complete answers (= 59.1 percent of those who started). Participants had the opportunity to watch an instruction video. Payments were administered by the panel provider via bank transfer and ranged from 2.90 Euro to 65 Euro, averaging 8.83 Euro. 

</div>

## Italy

<div style="text-align: justify">

In Italy, olive growers from the Apulia region (Southern area of the country) have been targeted. Note that the regional average olive farm size is approximately one hectare. With the help of local farm advisors, potential respondents were contacted and recruited via email or phone calls. The final sample consists of 130 olive growers. Data were collected via face-to-face interviews during summer 2021. Filter questions ensured that only active farmers with a prominent role in the business decisions could take part in the survey. Each respondent received a cash payment at the end of the experiment and was informed at the beginning of the exchange rate regarding the lottery values (mean=10.02 Euro, Minimum= 2.90 Euro, Max=65 Euro). 

</div>

## Netherlands

<div style="text-align: justify">

In the Netherlands, the target population consisted of arable farmers. A market research company administered the online survey and sent it out to a random sample of 5,000 email addresses of arable farmers from their database in July and August 2021. A reminder was sent a week after the first invitation. Filter questions ensured that only arable farmers with substantial decision-making power and farm ownership could take part. A video, explaining the experimental task, was available in Dutch. The survey was completed by 160 participants (out of whom 102 signed up for and received the payment), implying an effective response rate of approximately 3 percent. 115 farmers signed up for the debriefing. All participants had the opportunity to receive a payment by bank transfer which was administered with the help of the market research company. The average payment was 16.09 Euro (SD = 17.21 Euro, Minimum = 4.35 Euro, Maximum = 97.50 Euro). 

</div>


## Poland

<div style="text-align: justify">

In Poland, 57 farmers were recruited by five agricultural advisors in three voivodeships: Podlaskie (30), Pomorskie (5) and Łódzkie (22). Farmers were invited to take part in an online survey during meetings with their advisors that took place between September 20 and October 31, 2021. An additional 112 farmers were selected from a panel of a market research company (Ariadna). The company ran a separate profile survey, in which 40 thousand panelists living in rural areas were asked to spontaneously state their employment sector ('Agricultural' out of 21 sectors defined by Central Statistics Office in Poland) and type of occupation/employment agreement (farmers). Around 7,000 respondents who qualified were contacted with the link to the study on September 23, 2021. At the beginning of the survey, they were asked to confirm their previous responses (double spontaneous screening on employment sectors and occupations). 386 panelists opened the link, and 112 remained in the final sample. We asked about contact details. We informed participants that payments could only be administered after they sign a special form and send it back by scan or post to the University of Warsaw. On October 22, 2021, by individual emails/post (envelope with a return stamp), we requested such documents. The document contained a signature, name, surname and account number. Direct bank transfers were made by the University of Warsaw financial section to 94 farmers who had sent the necessary documents, using a rate of 0.05 PLN (approximately 0.01 EURO) per experimental currency unit. The average lottery result for all 169 participants was 39.70 PLN. The average of 94 payments transferred was 43 PLN (9.34 EUR); it ranged between 19.50 PLN (4.24 EU) and 90 PLN (19.56 PLN).

</div>


## Slovenia

<div style="text-align: justify">

In Slovenia, the target population were young farmers and young family members who actively engage in farming and are likely to take over their family farm in the upcoming years. Potential respondents were recruited via email and on farm and other events, which were organised or attended by the members of the Association of Slovenian Rural Youth between July and October 2021. The Association has about 3,000 members and the final sample consisted of 114 respondents. 88 respondents were interviewed face-to-face, whereas 26 respondents filled the survey on-line and thus had access to a video explaining the experimental task in Slovenian. The opportunity to receive a voucher for different products and services of the Association was offered to all participants, to which 93 responded by providing their email. The average payment was 9.15 Euro (ranging from 2.90 Euro to 45 Euro). 

</div>

## Spain

<div style="text-align: justify">

In Spain, the target population consisted of the members of two olive oil cooperatives in Andalusia. The cooperatives have 1,482 members and 132 of them responded to an invitation to an in-person meeting at the cooperative's premises (response rate 8.9%). During the meetings, instructions for the survey were explained following the structure of the questionnaire, including a screening of the video translated to Spanish. Each farmer responded individually to the survey on their mobile device, having access to all the instructions individually. All participants were compensated for their participation with a fixed payment of 10 Euros and a payment linked to their choices. The average total payment (including the show-up fee) was 15.70 euros (ranging from 5.80 to 36 Euro) with an average variable payment being 5.70 (from -4.20 Euro to 26 Euro). Participants could exchange their payment for olive oil at the cooperative's shop. 69% farmers signed up for the de-briefing. 

</div>

## Sweden

<div style="text-align: justify">

In Sweden, all registered farming businesses with an email address were part of the target population based on a list obtained from the Statistical Bureau of Sweden. 36,940 businesses met this criterion which is more than half of all registered farming businesses. Personalized invitation links to an online survey (programmed in Qualtrics) were sent to a simple random sample of 19,000 registered farm businesses with an email address in November and December 2021. Approximately five percent of the email addresses were invalid. The survey was completed by 218 respondents (209 or 96 percent of whom provided an email address to be eligible for payment), implying an effective response rate of approximately one percent. Out of all respondents, 188 (= 86 percent) signed up for the debriefing. One in ten participants received a payment by bank transfer which was administered with the help of a market research company. In total, 24 respondents were randomly selected for payment. The average payment was 1,365 SEK (132 Euro), ranging from 680 SEK (66 Euro) to 2,080 SEK (202 Euro).

</div>

\
\
\
\
\

\newpage

# Structural models with covariates

<div style="text-align: justify">

The following tables present coefficient estimates for the structural models from Tables 4 (EUT), 5 (EUT expo power), 6 (CPT) in the main text, but here the models include covariates (the seven common covariates discussed in the main text). To allow for an easy interpretation of the structural model parameters, all variables have been mean-centered (i.e., we use deviation from the sample mean). 

Note that there are fewer observations due to list-wise missing data for some of the covariates (recall that participants could choose not to respond to some of the demographic questions). Please also note that in some instances, models did not converge or that models may have converged at local maxima (e.g., Spain in the EUT model). This is because, many of the covariates are dummy variables (little variation in the independent variables) and there is limited variation in the dependent variable (respondents tend to cluster on some rows for their switch, see section 1 of this appendix). Taken together, in a small sample, this can lead to flat areas of the likelihood function which increases the risk of reaching local maxima or non-converging models. One could solve this problem for instance by dropping observations, co-variates, or changing starting values, but given the magnitude of this project, we have refrained from doing so.  


</div>




```{r}
load("storedResults/mlmodels.RData")

mlmodels_EU_cov_html <- lapply(mlmodels_EU_cov,maxlik_texreg)  
mlmodels_EX_cov_html <- lapply(mlmodels_EX_cov,maxlik_texreg)  
mlmodels_PT_cov_html <- lapply(mlmodels_PT_cov,maxlik_texreg)  

sh <- list(  digits = 3 , ci.force = TRUE , ci.test=NA , stars = numeric(0) ,  caption.above = TRUE, caption="" ) ## general settings used in all tables


```


\
\
\
\
\

\newpage


## Results over all samples in Expected Utility model with covariates (re-estimation of table 4 in main text)

```{r, warning=FALSE, results='asis' }

do.call(htmlreg, c(list(l=mlmodels_EU_cov_html ),sh)) 

```

\
\
\
\
\

\newpage


## Results over all samples in Exponential Power model with covariates (re-estimation of table 5 in main text)

```{r results='asis'}

do.call(htmlreg, c(list(l=mlmodels_EX_cov_html),sh))  


```

\
\
\
\
\

\newpage

## Results over all samples in Prospect Theory model with covariates (re-estimation of table 6 in main text)
 
```{r results='asis'}
 

do.call(htmlreg, c(list(l=mlmodels_PT_cov_html ) ,sh))  




```

\
\
\
\
\

# Mid-point approach

<div style="text-align: justify">

The mid-point approach is based on approximations of parameter values for lottery choices per individual. Each combination of lottery choices under monotonous switching is consistent with certain intervals for the three CPT parameters. Mid-points of these intervals are used to approximate the three parameters per individual. In the main text, the distribution of these approximations is displayed in figure 1. Here, we provide additional statistics for the pooled data and per sample (Summary statistics for mid-point approximations). Finally, we also provide higher resolution figures for the distribution of the three parameters per sample ('Plots').


</div>

\
\
\
\
\

\newpage 


## Summary statistics for mid-point approximations

The summary statistics for all countries exclude the sample from BJR2014.


### Mid-point approach summary statistics per sample

```{r, eval=TRUE}

midpoints %>% CreateAllFacet("Country") %>%  mutate(facet=forcats::fct_relevel(factor(facet,ordered = T),c(  "BJR2014") ) )%>% 
  select(facet, sigma_Mid, lambda_Mid, gamma_Mid) %>% rename("\u03c3" = "sigma_Mid", "\u03bb"="lambda_Mid", "\u03b3" = "gamma_Mid") %>% 
  group_by(facet) %>% 
  descr( show = c( "n"  , "mean", "md" , "sd","range"),out = "browser" )


```

\
\
\
\
\

\newpage

## Plots

The plots are similar to those from the main text but in a larger resolution. 


```{r}

graphs <- list()

ucnames<- c(sigma_Mid="\u03c3", lambda_Mid="\u03bb" ,gamma_Mid="\u03b3")

for (c in c("All Countries",levels(midpoints_backup$Country)) ) {

if(c!="All Countries")  midpoints<- midpoints_backup[midpoints_backup$Country==c,] else midpoints <- midpoints_backup[midpoints_backup$Country!="BJR2014",]



for (par in c("sigma_Mid", "lambda_Mid" ,"gamma_Mid" )) {
  
  
  
  p  = ggplot(midpoints, aes(x = 1, y = get(par))) + 
    ## add half-violin from {ggdist} package
    ggdist::stat_halfeye(
      ## custom bandwidth
      adjust = .5, 
      ## adjust height
      width = .6, 
      ## move geom to the right
      justification = -.2, 
      ## remove slab interval
      .width = 0, 
      point_colour = NA
    )  +
    geom_boxplot(
      width = .12,
      ## remove outliers
      outlier.color = NA ## `outlier.shape = NA` works as well
    ) +
    # add dot plots from {ggdist} package
    ggdist::stat_dots(
      ## orientation to the left
      side = "left",
      ## move geom to the left
      justification = 1.1,
      ## adjust grouping (binning) of observations
      binwidth = .00025
    ) +
    ## remove white space on the left
    coord_cartesian(xlim = c(0.5, NA)) +
    labs(title=paste0(c," ",ucnames[par]),
         x ="", y = ucnames[par]  ) +
    theme( axis.text.x=element_blank(), 
          axis.title.y=element_text(angle=0,vjust = 0.5) ,
          axis.ticks.x = element_blank() ,
          panel.background = element_rect( fill = "white") ,
          panel.grid.minor = element_line(color="lightgray") ,
          panel.grid.major = element_line(color="lightgray"))
  
  
  print(p)
  
  
  

  graphs[[paste0(c,par)]]=ggplotGrob(p)    
  
}

}
```

## Regression analysis

<div style="text-align: justify">

In this part, we present regression results to explain the heterogeneity in individual CPT parameters estimated with the mid-point approach. For each parameter ($\sigma$, $\lambda$, $\gamma$), an OLS regression is presented that estimates the effect of covariates on the size of these parameters.

</div>

### Parameter estimatess for CPT Model derived from mid-point approach ($\sigma$)

```{r, results='asis'}


htmlreg(MidpointRegressions[["Sigma"]] ,  caption = "",
        custom.coef.names = c("Constant", "Age", "NbChildren" , "Trust" , "FarmSize" , "LandOwned" , "IndivOwner" ) ,digits = 3 , ci.force = TRUE , ci.test=NA , stars = numeric(0) )
    

```

\
\
\
\
\

\newpage

### Parameter estimatess for CPT Model derived from mid-point approach ($\lambda$) 

```{r, results='asis'}


htmlreg(MidpointRegressions[["Lambda"]] ,  caption = "",
        custom.coef.names = c("Constant", "Age", "NbChildren" , "Trust" , "FarmSize" , "LandOwned" , "IndivOwner" ),digits = 3 , ci.force = TRUE , ci.test=NA , stars = numeric(0) )
    

```

\
\
\
\
\

\newpage

### Parameter estimatess for CPT Model derived from mid-point approach ($\gamma$) 

```{r, results='asis'}


htmlreg(MidpointRegressions[["Gamma"]] ,   caption = "",
        custom.coef.names = c("Constant", "Age", "NbChildren" , "Trust" , "FarmSize" , "LandOwned" , "IndivOwner" ),digits = 3 , ci.force = TRUE , ci.test=NA , stars = numeric(0) )
    

```

\
\
\
\
\

\newpage

# Additional robustness checks discussed in main text

## Reduced number of observations for the structural models

<div style="text-align: justify">

As in BJR2014, we re-estimated the structural models based on only observations next to the switching point. For example, if a respondent switched from A to B in lottery choice 7, we kept only the observations for lottery choices 6 and 7. If a respondent choose always lottery A or always lottery B, only one observation was kept.

</div>

```{r rob1}

load("storedResults/mlmodels_rob1.RData")

mlmodels_EU_cov_html <- lapply(mlmodels_EU_cov,maxlik_texreg)  
mlmodels_EX_cov_html <- lapply(mlmodels_EX_cov,maxlik_texreg)  
mlmodels_PT_cov_html <- lapply(mlmodels_PT_cov,maxlik_texreg) 

mlmodels_EU_html <- lapply(mlmodels_EU,maxlik_texreg)  
mlmodels_EX_html <- lapply(mlmodels_EX,maxlik_texreg)  
mlmodels_PT_html <- lapply(mlmodels_PT,maxlik_texreg)

sh <- list(  digits = 3 , ci.force = TRUE , ci.test=NA , stars = numeric(0) ) ## general settings used in all tables

```

\
\
\
\
\

\newpage

### Results over all samples for Expected Utility model (fewer observations per respondent) 

```{r, results='asis'}


do.call(htmlreg, c(list(l=mlmodels_EU_html , caption = ""),sh))  


```

\
\
\
\
\

\newpage

### Results over all samples for Expected Utility model with covariates (fewer observations per respondent)

```{r, results='asis'}



do.call(htmlreg, c(list(l=mlmodels_EU_cov_html , caption = ""),sh))  



```

\
\
\
\
\
\

\newpage

### Results over all samples for Exponential Power model (fewer observations per respondent)

```{r, results='asis'}
 

do.call(htmlreg, c(list(l=mlmodels_EX_html , caption = ""),sh))  



```

\
\
\
\
\
\

\newpage

### Results over all samples for Exponential Power model with covariates (fewer observations per respondent)

```{r, results='asis'}


do.call(htmlreg, c(list(l=mlmodels_EX_cov_html , caption = ""),sh))  
  


```

\
\
\
\
\
\

\newpage


### Results over all samples for CPT model (fewer observations per respondent)

```{r, results='asis'}

do.call(htmlreg, c(list(l=mlmodels_PT_html , caption = ""),sh))  


```

\
\
\
\
\
\

\newpage


### Results over all samples for CPT model with covariates (fewer observations per respondent)

```{r, results='asis'}

do.call(htmlreg, c(list(l=mlmodels_PT_cov_html , caption = ""),sh))  

```

\
\
\
\
\

\newpage

## Excluding speeders

<div style="text-align: justify">

In this robustness check, we excluded respondents who completed the survey in six minutes or less. We arbitrarily selected this cut-off based on our own testing of the questionnaire. Note that we apply this test only to online data collection modes. In other words, the face-to-face data collections in Austria, Spain, and Italy are excluded from this robustness test.

</div>

```{r rob2, results='asis'}


 load("storedResults/mlmodels_rob2.RData")

mlmodels_EU_cov_html <- lapply(mlmodels_EU_cov,maxlik_texreg)  
mlmodels_EX_cov_html <- lapply(mlmodels_EX_cov,maxlik_texreg)  
mlmodels_PT_cov_html <- lapply(mlmodels_PT_cov,maxlik_texreg) 

mlmodels_EU_html <- lapply(mlmodels_EU,maxlik_texreg)  
mlmodels_EX_html <- lapply(mlmodels_EX,maxlik_texreg)  
mlmodels_PT_html <- lapply(mlmodels_PT,maxlik_texreg)

sh <- list(  digits = 3 , ci.force = TRUE , ci.test=NA , stars = numeric(0) ) ## general settings used in all tables

```

\
\
\
\
\


\newpage 

### Results over all samples for Expected Utility model (speeders removed)

```{r , results='asis'}

do.call(htmlreg, c(list(l=mlmodels_EU_html , caption = ""),sh))  
```

\
\
\
\
\

\newpage 

### Results over all samples for Expected Utility model with co-variates (speeders removed)

```{r , results='asis'}
do.call(htmlreg, c(list(l=mlmodels_EU_cov_html , caption = ""),sh))  

```

\
\
\
\
\

\newpage

### Results over all samples for Exponential Power model (speeders removed)

```{r , results='asis'}
do.call(htmlreg, c(list(l=mlmodels_EX_html , caption = ""),sh))  

```


\
\
\
\
\

\newpage

### Results over all samples for Exponential Power model with covariates (speeders removed)


```{r , results='asis'}
do.call(htmlreg, c(list(l=mlmodels_EX_cov_html , caption = ""),sh))  

```


\
\
\
\
\

\newpage

### Results over all samples for CPT model (speeders removed)


```{r , results='asis'}
do.call(htmlreg, c(list(l=mlmodels_PT_html , caption = ""),sh))  


```


\
\
\
\
\

\newpage

### Results over all samples for CPT model with co-variates (speeders removed)


```{r , results='asis'}
do.call(htmlreg, c(list(l=mlmodels_PT_cov_html , caption = ""),sh))  
  

```

\
\
\
\
\

\newpage

## Excluding uncertain and random respondents


<div style="text-align: justify">

As a robustness test, we excluded respondents who answered with "fully agree" to at least one of the statements "My choices were random." and "It was difficult to understand the task." (see section 7 for summary statistics on these questions).

</div>


```{r rob3, results='asis'}

 load("storedResults/mlmodels_rob3.RData")

mlmodels_EU_cov_html <- lapply(mlmodels_EU_cov,maxlik_texreg)  
mlmodels_EX_cov_html <- lapply(mlmodels_EX_cov,maxlik_texreg)  
mlmodels_PT_cov_html <- lapply(mlmodels_PT_cov,maxlik_texreg) 

mlmodels_EU_html <- lapply(mlmodels_EU,maxlik_texreg)  
mlmodels_EX_html <- lapply(mlmodels_EX,maxlik_texreg)  
mlmodels_PT_html <- lapply(mlmodels_PT,maxlik_texreg)

sh <- list(  digits = 3 , ci.force = TRUE , ci.test=NA , stars = numeric(0) ) ## general settings used in all tables

```



\newpage

\
\
\
\
\

### Results over all samples for Expected Utility model (uncertain and random responses removed)


```{r, results='asis'}
do.call(htmlreg, c(list(l=mlmodels_EU_html , caption = ""),sh))  

```


\newpage

### Results over all samples for Expected Utility model with co-variates (uncertain and random responses removed)

```{r, results='asis'}
do.call(htmlreg, c(list(l=mlmodels_EU_cov_html , caption = ""),sh))  
```

\
\
\
\
\


\newpage

### Results over all samples for Expected Utility expo power model (uncertain and random responses removed)


```{r, results='asis'}

do.call(htmlreg, c(list(l=mlmodels_EX_html , caption = ""),sh))  
```

\
\
\
\
\

\newpage

### Results over all samples for Expected Utility expo power model with co-variates (uncertain and random responses removed)


```{r, results='asis'}

do.call(htmlreg, c(list(l=mlmodels_EX_cov_html , caption = ""),sh))  

```


\
\
\
\
\

\newpage

### Results over all samples for CPT model (uncertain and random responses removed)


```{r, results='asis'}

do.call(htmlreg, c(list(l=mlmodels_PT_html , caption = ""),sh))  

```

\
\
\
\
\

\newpage

### Results over all samples for CPT model with co-variates (uncertain and random responses removed)

```{r, results='asis'}

do.call(htmlreg, c(list(l=mlmodels_PT_cov_html , caption = ""),sh))  
 
```


\
\
\
\
\

\newpage



# Follow-up comprehension and assessment questions

Directly after the lottery choices, participants responded to three items on their comprehension and attitude towards the survey. Responses are on a 5-point scale ranging from strongly disagree to strongly agree.


\
\
\
\
\

\newpage

## Self-assessed difficulty in understanding the task 

```{r}
Understanding[[1]]
```


\
\
\
\
\

\newpage

## Self-assessed randomness of lottery choices

```{r}
Understanding[[2]]
```


\
\
\
\
\

 

\newpage

## Self-assessment of number of lottery choices

```{r}
Understanding[[3]]
```

\
\
\
\
\

\newpage

# Screenshots of survey instrument (example)


```{r}


names <- list.files(path = "surveyexample/", full.names = T)

# All defaults

#print(lapply(names, knitr::include_graphics))
knitr::include_graphics(names, dpi = 100)


```

\newpage

# Additional resources

The paper, this appendix and all other material are publicly available on the open science framework (OSF) webpage https://osf.io/hvmj6/. This includes the following resources:

- Pre-registration

- Questionnaires for all samples in English and local language as Qualtrics files

- Videos embedded in the questionnaires in all local languages

- Data via GitHub, accessible on OSF

- Code for statistical analysis, creation of tables and figures, and appendix via GitHub, accessable on OSF

- Ethics approval from the German Association of Experimental Economics










